Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})

### 2014-05-16 manuscript.tex
formatting for AJB cont.

\section*{Introduction}

@@

\section*{Methods}

\subsection*{Sampling and Genotyping}

@@

\subsection*{Genotyping Analysis} \jri{please drop scripts for bayenv and STRUCTURE into github} \lev{which scripts are you talking about? I used matt's for making structure chunks, and then just command line to run structure, same with BayEnv -- it was Tanjas covariance matrix and then just the basic bayenv commands} \jri{matt's scritp for structure should be up there. and even a readme documenting the commandline for bayenv and including the covariance matrix. basically whatever someone would need to be able to literally repeat what you did.}

@@

\subsection*{Sequence Analysis}

@@

\subsection*{Introgression Analysis}

@@

\section*{Results}

@@

\subsubsection*{Phenotyping}

@@

\section*{Discussion}

>>>>

\begin{centering}
\section*{INTRODUCTION}
\end{centering}

@@

\begin{centering}
\section*{MATERIALS AND METHODS}
\end{centering}

\mbh{from AJB formatting instructions: add name, city, spelled-out state (if in USA), and country of manufacturers/suppliers after brand names}

\subsection*{Sampling and genotyping}

@@

\subsection*{Genotyping analysis} \jri{please drop scripts for bayenv and STRUCTURE into github} \lev{which scripts are you talking about? I used matt's for making structure chunks, and then just command line to run structure, same with BayEnv -- it was Tanjas covariance matrix and then just the basic bayenv commands} \jri{matt's scritp for structure should be up there. and even a readme documenting the commandline for bayenv and including the covariance matrix. basically whatever someone would need to be able to literally repeat what you did.}

@@

\subsection*{Sequence analysis}

@@

\subsection*{Introgression analysis}

@@

\begin{centering}
\section*{RESULTS}
\end{centering}

@@

@@

\begin{centering}
\section*{DISCUSSION}
\end{centering}
